Adopting agile in the large: motivations, success factors and challenges

### 2014-05-08 journal/article.tex
Editing

The difficulty of agile and misunderstandings were also evident in cases where
the methods were customized badly. As by-the-book implementation often was not
feasible the agile method was tailored to suit the needs of the organization.
However, in some cases tailoring meant skipping some practices, which lead into
problems. In one case certain individuals were allowed to ignore some core
elements of Scrum, which came to turn the teams decision making into a variant
of command and control [P9].
Lewis and Neher [P29] describe how there was temptation to strip some practices
and enhance others. Previous attempts had proven that one of the reasons early
attempts of agile had failed was deviations from the process, because of which
the agile mindset did not take root [P29]. In a bad implementation customization
may lead to the team taking only practices that reflect their current needs, and
therefore failing to achieve a real change in process and mindset [P9, P46].

@@

Many cases reported that introducing agile practices soon yielded improvements
on the team level, but as a part of a large transformation teams needed to
change their external behavior also.
The initial success was followed by challenges when the teams needed to work as
parts of the larger surrounding orgaization [P13, P17, P24]. Introducing agile
had created flexibility on a team level, but it could not be fully utilized as
the surrounding organization was not responsive enough [P26].
There were dependencies between teams in the agile model as well, and the
dependencies made managing development difficult [P9, P10].

>>>>

The difficulty of agile and misunderstandings were also evident in cases where
the methods were customized badly. As by-the-book implementation often was not
feasible the agile method was tailored to suit the needs of the organization.
However, in some cases tailoring meant skipping some practices, which lead into
problems. In one case certain individuals were allowed to ignore some core
elements of Scrum, which came to turn the teams decision making into a variant
of command and control [P9].
Lewis and Neher [P29] describe how there was temptation to strip some practices
and enhance others. Previous attempts had proven that one of the reasons early
attempts of agile had failed was deviations from the process, because of which
the agile mindset did not take root [P29]. In a bad implementation customization
may lead to the team taking only practices that reflect their current needs, and
therefore failing to achieve a real change in process and mindset [P9, P46].
Another example of bad customization that counteracts change is replacing agile
vocabulary by favoring familiar terminology from the old model [P44].

@@

Many cases reported that introducing agile practices soon yielded improvements
on the team level, but as a part of a large transformation teams needed to
change their external behavior also.
The initial success was followed by challenges when teams needed to work with
other teams and as parts of the larger surrounding orgaization [P13, P17, P24].
Introducing agile had created flexibility on a team level, but it could not be
fully utilized as the surrounding organization was not responsive enough [P26].
There were dependencies between teams in the agile model as well, and the
dependencies made managing development difficult [P9, P10].
